---
title: "Submission 1"
output: html_notebook
---

# 0 Introduction

0.1 SPDR GLD was selected for a gold etf fund: https://etfdb.com/etf/GLD/#etf-ticker-profile

0.2 iSharesMSCI australia etf was selected for an equity etf: https://www.ishares.com/us/products/239607/ishares-msci-australia-etf


# 1 Data Importing
1.1 Treasury yield curve data was imported from treasury.gov:

```{r}
yc <- read.csv(file = 'data/yieldcurve.csv')
yc
```

1.2 GLD etf data was imported from yahoo finance:

```{r}
gld <- data.frame(read.csv(file = 'data/GLD.csv'))
gld
```

1.2 GLD etf data was imported from yahoo finance:

```{r}
ewa <- read.csv(file = 'data/EWA.csv')
ewa
```



# 2 Data Processing

2.1 The daily returns are computed for the gold and equity ETFs:
```{r}

gen_logret <- function(df){
  df$logret = log(df$Adj.Close/c(0, head(df$Adj.Close, -1)))
  df <- df[-1,]
  return(df)
}
gld <- gen_logret(gld)
gld

ewa <- gen_logret(ewa)
ewa

```


# 3 Data Summaries


# 4 Graphing


# 5 Fitting the Yield Curve


# 6 Modeling Prices


# 7 Modeling Volatility


# 8 Correlation