---
title: "Submission 1"
output: html_notebook
---

# 0 Introduction

```{r}
library(data.table)
library(ggplot2)
library(xts)
```

0.1 SPDR GLD was selected for a gold etf fund: https://etfdb.com/etf/GLD/#etf-ticker-profile

0.2 iSharesMSCI australia etf was selected for an equity etf: https://www.ishares.com/us/products/239607/ishares-msci-australia-etf


# 1 Data Importing
1.1 Treasury yield curve data was imported from treasury.gov:

```{r}
csvToXTS <- function(filename){
  yc <- data.table(read.csv(file = filename))
  yc[[1]] <- as.Date(yc[[1]])
  dates = yc[[1]]
  yc <- subset(yc, select = -c(Date) )
  yc <- xts(yc, order.by=dates)
  return(yc)
}

yc <- csvToXTS('data/yieldcurve.csv')
head(yc)
```

1.2 GLD etf data was imported from yahoo finance:

```{r}
gld <- csvToXTS('data/GLD.csv')
head(gld)
```

1.2 GLD etf data was imported from yahoo finance:

```{r}
ewa <- csvToXTS('data/EWA.csv')
head(ewa)
```



# 2 Data Processing

2.1 The daily returns are computed for the gold and equity ETFs:
```{r}

gen_logret <- function(df){
  df$logret = log(df$Adj.Close/c(0, head(df$Adj.Close, -1)))
  df <- df[-1,]
  return(df)
}
gld <- gen_logret(gld)
head(gld)

ewa <- gen_logret(ewa)
head(ewa)

```


# 3 Data Summaries
```{r}
#nov1 = '2019-11-01'
oct = '/2019-10-31'
nov = '2019-11-01/'
summaries <- data.table(
  ticker   = c('yc2', 'yc3', 'yc5', 'yc7', 'yc10', 'yc30', 'gld', 'ewa'),
  mean_oct = c( mean(yc[oct]$y2), 
                mean(yc[oct]$y3), 
                mean(yc[oct]$y5), 
                mean(yc[oct]$y7), 
                mean(yc[oct]$y10), 
                mean(yc[oct]$y30), 
                mean(gld[oct]$Adj.Close), 
                mean(ewa[oct]$Adj.Close)),
  sd_oct   = c( sd(yc[oct]$y2),
                sd(yc[oct]$y3),
                sd(yc[oct]$y5),
                sd(yc[oct]$y7),
                sd(yc[oct]$y10),
                sd(yc[oct]$y30),
                sd(gld[oct]$Adj.Close),
                sd(ewa[oct]$Adj.Close)),
  mean_nov = c( mean(yc[nov]$y2),
                mean(yc[nov]$y3),
                mean(yc[nov]$y5),
                mean(yc[nov]$y7),
                mean(yc[nov]$y10),
                mean(yc[nov]$y30),
                mean(gld[nov]$Adj.Close),
                mean(ewa[nov]$Adj.Close)),
  sd_nov   = c( sd(yc[nov]$y2),
                sd(yc[nov]$y3),
                sd(yc[nov]$y5),
                sd(yc[nov]$y7),
                sd(yc[nov]$y10),
                sd(yc[nov]$y30),
                sd(gld[nov]$Adj.Close),
                sd(ewa[nov]$Adj.Close))
) 
summaries
```

# 4 Graphing
```{r}
fourpt1 <- ggplot(data = yc, aes(x = Index)) + 
  geom_point(aes(y=y2, color='2-year')) +
  geom_point(aes(y=y3, color='3-year')) +
  geom_point(aes(y=y5, color='5-year')) +
  geom_point(aes(y=y7, color='7-year')) +
  geom_point(aes(y=y10, color='10-year')) +
  geom_point(aes(y=y30, color='30-year')) +
  labs(colour="US Treasury Yields",x="Date",y="Yield (%)") +
  scale_color_manual(values = c("red","blue","green","orange","purple","brown"))
print(fourpt1)
```

# 5 Fitting the Yield Curve


# 6 Modeling Prices

Nelson-Siegel-Svensson yield curve formula for the forward rate:

$$\begin{array}{ccc}
y_t(T) = \beta_{0} + \beta_{1} \exp\left( -\frac{T}{\tau_1} \right) + \beta_2
\frac{T}{\tau_1} \exp \left( -\frac{T}{\tau_1} \right) + \beta_3
\frac{T}{\tau_2} \exp \left( -\frac{T}{\tau_2} \right)
\end{array}$$


```{r}
MATURITY_BASES = c(2, 3, 5, 7, 10, 30)
A <- Svensson(yc, MATURITY_BASES )
A
Svensson.rate <- Srates( A, MATURITY_BASES, "Spot" )
Svensson.rate
```
5.4 Significant changes to paramenters:
It appears from the parameter graph, during the month of october, beta_3 rises from -20 to around -1. then during november it drops back to -20. Also, tau2 experiences changes. Around the end of october, value occasionally drop from 15 down to 3. It is those same days--october 28th and oct 29th that experience higher then average yield curve--meaning the structure of the curve didnt change but the entire curve rose upward.

```{r}
idx = index(yc)
{
  for (i in seq_along(idx)){
  plot(MATURITY_BASES, Svensson.rate[i,],main=paste("Fitting Svensson yield curve", idx[i]),xlab=c("Pillars in years"), type="l", col=3, ylim=range(1.3:2.5))
  lines(MATURITY_BASES, yc[i,],col=2)
  legend("topleft",legend=c("fitted yield curve","observed yield curve"),col=c(3,2),lty=1)
}
} 

{
  plot(MATURITY_BASES, Svensson.rate[10,],main=paste("Fitting Svensson yield curve", idx[10]),xlab=c("Pillars in years"), type="l", col=3, ylim=range(1.3:2.5))
  lines(MATURITY_BASES, yc[10,],col=2)
  legend("topleft",legend=c("fitted yield curve","observed yield curve"),col=c(3,2),lty=1)
}

plot(A, legend.loc="topleft")

```
# 7 Modeling Volatility


# 8 Correlation

