---
title: "Submission 1"
output: html_notebook
---

# 0 Introduction

```{r}
library(data.table)
```

0.1 SPDR GLD was selected for a gold etf fund: https://etfdb.com/etf/GLD/#etf-ticker-profile

0.2 iSharesMSCI australia etf was selected for an equity etf: https://www.ishares.com/us/products/239607/ishares-msci-australia-etf


# 1 Data Importing
1.1 Treasury yield curve data was imported from treasury.gov:

```{r}
yc <- data.table(read.csv(file = 'data/yieldcurve.csv'))
yc[[1]] <- as.Date(yc[[1]])
yc
```

1.2 GLD etf data was imported from yahoo finance:

```{r}
gld <- data.table(read.csv(file = 'data/GLD.csv'))
gld[[1]] <- as.Date(gld[[1]])
gld
```

1.2 GLD etf data was imported from yahoo finance:

```{r}
ewa <- data.table(read.csv(file = 'data/EWA.csv'))
ewa[[1]] <- as.Date(ewa[[1]])
ewa
```



# 2 Data Processing

2.1 The daily returns are computed for the gold and equity ETFs:
```{r}

gen_logret <- function(df){
  df$logret = log(df$Adj.Close/c(0, head(df$Adj.Close, -1)))
  df <- df[-1,]
  return(df)
}
gld <- gen_logret(gld)
gld

ewa <- gen_logret(ewa)
ewa

```


# 3 Data Summaries
```{r}
nov1 = '2019-11-01'
summaries <- data.table(
  ticker   = c('yc2', 'yc3', 'yc5', 'yc7', 'yc10', 'yc30', 'gld', 'ewa'),
  mean_oct = c( mean(yc[Date<nov1]$y2), 
                mean(yc[Date<nov1]$y3), 
                mean(yc[Date<nov1]$y5), 
                mean(yc[Date<nov1]$y7), 
                mean(yc[Date<nov1]$y10), 
                mean(yc[Date<nov1]$y30), 
                mean(gld[Date<nov1]$Adj.Close), 
                mean(ewa[Date<nov1]$Adj.Close)),
  sd_oct   = c( sd(yc[Date < nov1]$y2),
                sd(yc[Date < nov1]$y3),
                sd(yc[Date < nov1]$y5),
                sd(yc[Date < nov1]$y7),
                sd(yc[Date < nov1]$y10),
                sd(yc[Date < nov1]$y30),
                sd(gld[Date < nov1]$Adj.Close),
                sd(ewa[Date<nov1]$Adj.Close)),
  mean_nov = c( mean(yc[Date>=nov1]$y2),
                mean(yc[Date>=nov1]$y3),
                mean(yc[Date>=nov1]$y5),
                mean(yc[Date>=nov1]$y7),
                mean(yc[Date>=nov1]$y10),
                mean(yc[Date>=nov1]$y30),
                mean(gld[Date>=nov1]$Adj.Close),
                mean(ewa[Date>=nov1]$Adj.Close)),
  sd_nov   = c( sd(yc[Date>=nov1]$y2),
                sd(yc[Date>=nov1]$y3),
                sd(yc[Date>=nov1]$y5),
                sd(yc[Date>=nov1]$y7),
                sd(yc[Date>=nov1]$y10),
                sd(yc[Date>=nov1]$y30),
                sd(gld[Date>=nov1]$Adj.Close),
                sd(ewa[Date>=nov1]$Adj.Close))
) 
summaries
```

# 4 Graphing


# 5 Fitting the Yield Curve


# 6 Modeling Prices


# 7 Modeling Volatility


# 8 Correlation